\documentstyle[fancybox]{article}
\input{icpcpl}
\input{acm}
\input{boloon}
\input{trophy}
\input{picone}
\input{pictwo}
\input{isiran}

\font\arm=arm25
\font\tfont=cmssbx10 scaled 1400
\font\sfont=cmssdc10 scaled 1400
\font\addfont=cmssi9
\newfont{\bigman}{cmss17}
%\fancypage{%
\setlength{\fboxsep}{5mm}
%\fbox}{}
\hyphenpenalty=1000
\pagestyle{empty}

\newenvironment{ilist}{     %itemized list with bullete
\begin{list}{$\bullet$}{\rightmargin=0mm\leftmargin=4mm
    \labelwidth=2mm\labelsep=2mm\setlength{\parsep}{\parskip}
    \setlength{\listparindent}{\parindent}
    }}{\end{list}}

\newcounter{mnum}
\newenvironment{mlist}{\setcounter{mnum}{0}     % 1) 2) 3)
\begin{list}{\arabic{mnum}.}{\usecounter{mnum}\rightmargin=0mm\leftmargin=4mm
    \labelwidth=4mm\labelsep=2mm\setlength{\parsep}{\parskip}
    \setlength{\listparindent}{\parindent}
    }}{\end{list}}

%\renewenvironment{description}{
%\begin{list}{\bf}{\rightmargin=0mm\leftmargin=6mm
%    \labelwidth=4mm\labelsep=2mm\setlength{\parsep}{\parskip}
%    \setlength{\listparindent}{\parindent}
%    }}{\end{list}}


\newlength{\myleng}
\newenvironment{myshbox}
    {\noindent\begin{Sbox}%
      \setlength{\fboxsep}{3mm}
      \setlength{\myleng}{70mm}%
      \addtolength{\myleng}{-2\fboxsep}%
      \addtolength{\myleng}{-2\fboxrule}%
      \begin{minipage}{\myleng}}%\begin{center}}%
{%\end{center}
\end{minipage}\end{Sbox}\shadowbox{\TheSbox}}%

\newenvironment{myfbox}
    {\noindent\begin{Sbox}%
      %\setlength{\fboxsep}{5mm}
      \setlength{\myleng}{79mm}%
      %\addtolength{\myleng}{-2\fboxsep}%
      %\addtolength{\myleng}{-2\fboxrule}%
      \begin{minipage}{\myleng}}%\begin{center}}%
{%\end{center}
\end{minipage}\end{Sbox}\fbox{\TheSbox}}%



\textwidth=297.3mm
\textheight=210cm
%\oddsidemargin=-26.7mm
\oddsidemargin=-25.4mm
\topmargin=-28.5mm




\newsavebox{\pageone}
\savebox{\pageone}{
\begin{myfbox}
\vbox to 18cm{
\vfill
\vspace*{1mm}
\centerline{\setacm\kern1cm\raise-13.5mm\hbox{\arm a}}
\vspace*{5mm}
\centerline{\seticpcpl}
\vfill
\centerline{\setisiran}
\vfill
\begin{center}
{\tfont Asia Region, Tehran Site } \\[5mm]
{\sfont Computer Engineering Department}\\[1mm]
{\sfont Sharif University of Technology}\\[1mm]
{\sfont Tehran, Iran}\\[3mm]
{\sfont November 7-8 2001  (Aban 16-17, 1380)}
\end{center}
}
\end{myfbox}
}


\newsavebox{\pagetwo}
\savebox{\pagetwo}{
\begin{myfbox}
\vbox to 18cm{
\centerline{{\addfont In The Name of God}}
\vfill
\parindent=5mm
\section*{\bigman The Contest}
%\baselineskip=0.95\baselineskip
The\, ACM\, International\,  Collegiate\,  Programming  Contest (ACM/ICPC)
is the largest programming contest
among university and college students 
in the world.
This contest was initiated 25 years ago by
ACM  and seeks to 
engage academics and the information technology industry in 
shining the spotlight on the next generation of computing professionals 
and scholars, and to encourage the development of and
to recognize excellent team work, programming skills, and problem-solving 
talent.  

\indent
ACM (Association for Computing Machinery), funded in 1947, is the world's first 
educational and scientific computing society

\indent
The contest is a two-tiered competition among teams of students representing
institutions of higher education. Teams first compete in the regional contests
held around the world from September to November each year. The winning
team from each regional contest advances to the ACM/ICPC 
World Finals, normally held the following
March to mid-April. Additional high-ranking teams may be invited to the
World Finals as wild card teams.

Last year 2700 teams from 1079 universities of 70 countries
participated in the regional contests around the world. 64 teams
from 22 countries advanced to the World Finals in Vancouver, Canada,
among which 14 teams were from Asian countries. 

\vspace*{2mm}
\noindent
\begin{minipage}{4cm}
\parindent=5mm

\indent 
82 teams participated in Tehran contest
last year and two teams from Sharif University of Technology (SUT) and
Ferdowsi University of Mashad advanced to the 2001 World Finals. The
team from SUT was awarded a prestigious silver medal and ranked 9th overall and 2nd among 
all  Asian teams.
\end{minipage}
\hfill \settrophy
\vfill
}
\end{myfbox}
}



\newsavebox{\pagethree}
\savebox{\pagethree}{
\begin{myfbox}
\vbox to 18cm{
\parindent=5mm
\section*{\bigman Tehran Site}

For the third year, Sharif University of Technology 
will be hosting
the ACM/ICPC regional contest as one of the 8 sites in Asia.
Other sites are Dhaka in Bangladeh, Kanpur in India, Hakodate
in Japan, Shanghai in China, Taejon in Korea, Hong Kong, Singapore, and Taiwan.

%\vspace*{1mm}
%\noindent
%\begin{minipage}{4.5cm}
%\parindent=5mm\indent
\indent
The Tehran contest is scheduled to be held in 
SUT during
7-8 November 2001 (Aban 16-17, 1379).  We are expecting  about
80 teams of university  students from Iran and
countries in the west of Asia and the Middle East.
%\end{minipage}
%\hfill\setacmbloo
%\vspace*{1mm}

%\indent
%Asia region director will be present in the contest
%as the ACM representative.

\indent
The winning teams of Tehran contest will  automatically
advance to  the 26th
ACM/ICPC world finals to be held in Hawaii, USA, in March 20-24, 2002.
ACM and IBM will bear part of the travelling expenses
(up to US\$4000) for each advancing team.



\section*{\bigman Computing Environment}
Each team will use a single  workstation with environment
similar to the Word Finals. 
Delphi and
C++ are the available programming languages. The details of
the programming environment will be available in the contest website.



\vfill
\begin{center}
\setpicone
\end{center}
\vfill

}
\end{myfbox}
}




%-------------------------------------
\newsavebox{\pagefour}
\savebox{\pagefour}{
\begin{myfbox}
\vbox to 18cm{ %was 18
\section*{\bigman Summary of Rules and Judging}
{\baselineskip=0.93\baselineskip
\begin{ilist}
\itemsep=1mm
\item
Each team consists of up to three contestants. Each contestant must be a
student enrolled in a university.
At most one contestant of each team may hold a B.S. degree.

\item Each team can participate in at most two regional contests in any Asian site each year.

\item Only one team from a given institution may advance to the World Finals.

\item A special prize will be awarded to the best all-girl team and a slot in the World Finals 
may be given  to best such team in Asia.
\item
Contestants may bring resource materials such as books, manuals, and
program listings. Contestants may not bring any machine-readable
versions of software or data.

\item Eight or nine problems will be posed in English to be solved in 5 hours.

\item
Each submitted solution to a problem is
judged as accepted or rejected by a judge, and the team is notified of the
results online.


\item
Teams are ranked according to the most problems solved.
Teams with the same number of solved problems
are ranked by the least total time.
The total time is the sum of the time consumed for each \underline{solved} problem. 
This is  the time elapsed from the beginning of the
contest to the submittal of the accepted run plus 20 penalty minutes for
every rejected run for that problem regardless of submittal time.
\end{ilist}


\section*{\bigman Problem Selection}
The scientific committee is responsible for preparing the contest problems
which are selected from those proposed by its
member and received from the participating teams. 
All universities are asked to contribute to this important task.
A call for problem proposal will be sent out.

\hspace*{3mm}
So far as possible, the problems will avoid
dependence on detailed knowledge of a particular application area or
programming language.




%\newpage



}}
\end{myfbox}
}




%-------------------------------------
\newsavebox{\pagefive}
\savebox{\pagefive}{
\begin{myfbox}
\vbox to 18cm{
%\begin{description}
%\item[ ] \hspace*{5mm} 
%\end{description}

%\vfill
%\newpage


\section*{\bigman Registration Steps}
{\baselineskip=0.94\baselineskip
\begin{mlist}
\itemsep=1mm
\item Register your teams  as early as possible
   at  site: {\tt http://www.baylor.edu/acmicpc}. 
   Follow the registration link.  The names of the team members can be finalized
   later.
\item Send (or fax) the receipt of registration fee payment (this must be
      received by the first deadline to use the discount fee). Additional
      team registrations is allowed after early registrations are complete.
\item By the final deadline, send us an official letter from your university
      officials containing the names of the participating team
      members.
\item Finalize your online registration (names, addresses, etc.) by
     the mentioned deadline.
\end{mlist}


\section*{\bigman Limits on the Number of Teams}
There is a limit of two teams from each university, and a limit on 
the total number of teams that we can accept (about 80).  Universities that had a team 
with rank below 15 in  last contest, can register  more teams with our 
prior approval.


\section*{\bigman Deadlines}
\begin{description}
\itemsep=1mm
\item[Sept 13  (Shahrivar 22):]  \ \\
         Deadline to use the discount registration fee for local teams.
         A copy of the payment receipt should be received by this date.
         
\item[October 11 (Mehr 19):]  \ \\
         Deadline for registration of local teams at the ACM/ICPC office. 
         All documents must be received by this date.
         Registration may be closed after this deadline.


\item[October 21 (Mehr 30): ]  \ \\
         Online registration of ALL teams 
         should be complete by this date.

\item[October 1:] Participation confirmation for foreign teams.
\end{description}

\vfill
}}
\end{myfbox}
}






%-------------------------------------------------------------

\newsavebox{\pagesix}
\savebox{\pagesix}{
\begin{myfbox}
\vbox to 18cm{


\section*{\bigman  Registration Fees}

%The registration fees for each team:

\noindent
%\begin{minipage}{7cm}
\begin{center}
\small
\begin{tabular}{|l|c|c|}
\hline
Fee for  &     Sept 13, 2001  & Oct 22, 2001  \\   
each team       &   (Shahrivar 22)  & (Mehr 31) \\ \hline\hline
From Iran &  250,000 Rials  & 350,000 Rials \\ \hline
From Abroad%\footnote{
%Registration fees can be waived for 
%foreign teams from  certain neighboring countries.
%}
%  &      \$50  &      \$50 \\ \hline
   &      Free  &     Free  \\ \hline
\end{tabular}
\end{center}
%\end{minipage}

{\baselineskip=0.94\baselineskip
Local registration fees should be paid to account \#: 
727.65, Bank Markazi Iran, in the name of the Sharif University of Technology. 

\vspace*{-1mm}
\section*{\bigman Foreign Teams}
Most foreign teams  need visas for entering into Iran. These
teams should prepare well in advance and send us all visa correspondence by 
Oct.~1.

\vspace*{-1mm}
\section*{\bigman  Travel Fund}
Each foreign team is paid some travel fund of at least \$200.00 by the ACM.

\vspace*{-1mm}
\section*{\bigman  Accommodations}
There is no accommodation available in the university at the time of contest.
Iranian teams should take care of their own accommodations. We can help
them with hotel reservations, if needed. We will make hotel reservations
for foreign teams.



}
\vfill

\begin{center}
\setpictwo
\end{center}

}
\end{myfbox}
}


%-------------------------------------------------------------------

\newsavebox{\pageseven}
\savebox{\pageseven}{
\begin{myfbox}
\vbox to 18cm{

\section*{\bigman Steering Committee}
\begin{description}
\baselineskip=.95\baselineskip
\item[Honorary Chair:] \ \\
       Prof. Saeed Sohrabpour, Chancellor, \\ Sharif University
     of Technology 
\item[Asia Region Director:] \ \\
      Prof. C. J. Hwang,  Computer Science dept.,
                            South West Texas State University, USA
\item[Tehran Site Director:] \ \\ Dr. Mohammad Ghodsi
\item[Department Chair:] \ \\ Dr. Ghassem Miremadi
%\item[Executive Committee Chair:] \ \\  
%             Dr. Hassan Mirian

\item[Scientific Committee:] \ \\ 
             Dr. Rasool Jalili, Chair \\
             Mr. Ramtin Khosravi, Chief Judge \\
             Dr. Mohammad Ghodsi \\
             Mr. Ghassem JaberiPur, \\
             Mr. Bahman Pourvatan,  \\
             Mr. Farshad Rostamabadi, \\
             Mr. Bashir Sajjad, \\
             Mr. Ehsan ChiniForooshan, \\
             Mr. Mehdi Mirzazadeh, \\
             Mr. Mohammad Safari

%\item[Chief Judge:] \ \\ 
%             Mr. Ramtin Khosravi


\item[System:] \ \\ 
             Mr. Mohammad H. Khansari, Chair
             Mr. Kamran Bavar, system

\item[Executive Director:] \ \\  
             Mr. Hooshangnia

\item[Public Relations and Publications:] \ \\ 
             Mr. Hashem Habibi, Chair,\\
             Mrs. Shahindokht Shahnazi , \\
             Mr. Masoud Mohajer, \\
             Mr. Mohsen Iranfard

\item[International  Relations:] \ \\ 
             Dr. Ali Movaghar

\item[Office:] \ \\ 
           Mrs. Shahindokht Shahnazi 
                  
\end{description}
\vfill
%{\tiny
%SUT: Sharif University of Technology \\[-2mm]
%AKUT: AmirKabir University of Technology \\[-2mm]
%IUST: Iran University of Science and Technology 
%}

}
\end{myfbox}
}



\newsavebox{\pageeight}
\savebox{\pageeight}{
\begin{myfbox}
\vbox to 18cm{

\section*{\bigman Contact}

\hbox{\hss
\begin{myshbox}
\addfont
ACM/ICPC Tehran Site, \\
Computer Engineering Department, \\
Sharif University of Technology, \\
P.O.Box 11365-9517, Tehran, Iran. \\
Phone: +98 21 602-2714, \\ Fax: +98 21 600-5616/601-2983 \\
Email: acmicpc@sharif.ac.ir, \\
Homepage:   http://sharif.ac.ir/\char'176 acmicpc 
\end{myshbox}\hss}
\par
\noindent{\small\it More information  can be found from
the ACM main site at
{\tt http://www.baylor.edu/acmicpc}.}
\vfil
\centerline{\setboloon}
\vfil
\noindent\hspace{2mm}
\begin{minipage}{\textwidth}
\begin{center}
{\bigman  Main Supporter} \\
\vspace*{3mm}
Isiran Company \\
\vspace*{4mm}
{\bigman  Other Supporters} \\
\vspace*{3mm}
\small
 Ministry of Science, Research, and Technology, \\
 Iran High Council of Informatics,  \\
 Iran Telecommunication Research Center, \\
 Ministry of Telecommunications, \\
 Tehran Municipality 
 
\end{center}
\end{minipage}
\vfil
}
\end{myfbox}
}



\newsavebox{\emptypage}
\savebox{\emptypage}{
\begin{myfbox}
\vbox to 18cm{
\ \ 
\vfill
\ \ 
}
\end{myfbox}
}



\begin{document}


%\hbox to \hsize{\kern3.8mm\usebox{\pagetwo}\kern7.6mm\usebox{\pagethree}\kern7.6mm\usebox{\pagefour}\hfil}
%\hbox to \hsize{\kern3.8mm\usebox{\pagetwo}\kern7.5mm\usebox{\pagethree}\kern7.5mm\usebox{\pagefour}\hfil}
\hbox to \hsize{\hfil\usebox{\pagetwo}\hfil\hfil\usebox{\pagethree}\hfil\hfil\usebox{\pagefour}\kern2mm\hfil}

\newpage
\hbox to \hsize{\hfil\usebox{\pageeight}\hfil\hfil\usebox{\pagesix}\hfil\hfil\usebox{\pageseven}\kern2mm\hfil}


\newpage
\hbox to \hsize{\hfil\usebox{\pagefive}\hfil\hfil\usebox{\emptypage}\hfil\hfil\usebox{\emptypage}\hfil}


\newpage
\hbox to \hsize{\hfil\usebox{\pageone}\hfil\hfil\usebox{\emptypage}\hfil\hfil\usebox{\emptypage}\hfil}


\end{document}